Characterizing subarctic biomes for land surface modeling of pollution and climate risk.

### 2021-02-09 VegOzone.tex
Moved in text web addresses to bibliography

\subsection{NIBIO Environment Centre Svanhovd}
\label{subsec:svanhovd}
"Svanhovd is located beside the Pasvik river, in the middle of the wedge of Norwegian land separating Russia and Finland in the north. It is where the eastern Siberian taiga meets the western Boreal forest. [...] Svanhovd was originally established as a State Demonstration and Experimental Farm in the 1930's, in order to expand agriculture in Pasvik valley [...]" -- \href{https://www.nibio.no/en/about-eng/addresses/northern-norway/svanhovd}{NIBIO web page, last accessed March 2020}.

@@

\subsubsection{Atmospheric monitoring}
\label{subsubsec:atmo_svanvik}
For the growing seasons 2018/19, monitoring data of key variables (temperature, pressure, precipitation, and ozone) have been obtained from \href{luftkvalitet.no}{luftkvalitet.no} which is operated by NILU.

All agrometeorological variables including temperature and precipitation are available from September 1992 to present day (LandbruksMeteorologisk Tjeneste provided by NIBIO -- \href{https://lmt.nibio.no/}{lmt.nibio.no}, note the station name here is Pasvik).

@@

\subsubsection{Ozone garden}
\label{subsubsec:ozone_garden}
{\bf TODO: Details about the ozone garden and observed damage on ozone sensitive plants. We will need to come back to this in the discussion section after the Do3se modeling part.} \emph{Author: Ane/Aud -- pictures are welcome, just upload them on overleaf or send them to me.}
\begin{figure}
  \includegraphics[width=8.3cm]{IMG_7739.JPG}
  \caption{Clover in the Svanhovd ozone garden. The plants had to be secured against herbivores with a wire-mesh fence. The plants shown are approximately $6-12\,\unit{cm}$ in height.}
\end{figure}

@@

\subsubsection{Surface ozone observations}
\label{subsubsec:ebas}
All surface ozone observations used in this study are available from the EBAS database operated by NILU (\href{http://ebas.nilu.no/}{ebas.nilu.no}). In Table~\ref{tab:ebas_obs}, we give an overview over the exact locations and time range of operational data taking. All stations with available long term observations are located on higher ground than Svanhovd which will result in higher surface ozone concentrations in comparison as ozone abundance, in general, decreases with decreasing altitude in the absence of local precursors \citep[e.g.,][]{AB:Klingberg2009}. The periphery vegetation at all sites is similar and consists mainly of pine forests, birch, and heath. However, at close vicinity it varies substantially. Ozone measurements at Pallas are taken on top of mount Sammaltunturi $100\,\unit{m}$ above tree line (pine forest) and mainly consists of low vascular plants, mosses, and lichen \citep{BER:Hatakka2003}. At Svanhovd, the ozone measurements are taken amidst a meadow surrounded by agriculturally managed herbaceous plants and grass (c.c. Fig.\ref{fig:svanhovd_research_station}).

@@

Details of reanalysis data sets referred to in this work are listed in Table~\ref{tab:ozone_rea}.
There are two global reanalysis products available at the European Centre for Medium-Range Weather Forecasts (ECMWF) that include atmospheric tracers, in particular ozone (MACC and CAMSRA) \citep{ACP:Inness2013, ACP:Inness2019}. The temporal as well as spatial resolution of these reanalysis products is rather coarse: 3-hourly and $0.75^\circ\times 0.75^\circ$ or roughly $29.3\,\unit{km}\times 83.4\,\unit{km}$ at the location of Svanvik, respectively. In addition, higher resolution surface ozone reanalysis for whole Europe is available from Copernicus service for regional air quality control ({\bf TODO: From May 31st on through the CAMS Atmosphere Data Store (ADS)}). The regional air quality model reanalysis ensemble (CAMS regional Ensemble) is based on nine European state-of-the-art numerical air quality models ({\bf TODO: Reference -  https://atmosphere.copernicus.eu/documentation-regional-systems, last accessed April 2020}). The ensemble mean is at fairly high spatial and temporal resolution compared to the global reanalysis from ECMWF: $0.1^\circ\times 0.1^\circ$ or roughly $3.9\,\unit{km}\times 11.1\,\unit{km}$ and 1-hourly, respectively. The covered time periods differ and no data are available for before the turn of the millennium. The CAMSRA and CAMS Regional Air Quality ensemble mean are available in near real time, but only former covers a period of sufficient length for climate analysis (2003 -- present). All reanalyses use different but, at that time, latest versions of the operational weather forecast system (OpenIFS) from ECMWF. They differ substantially in the assimilated observational ozone data. The MACC reanalysis assimilates only satellite derived tropospheric column ozone (TC), while CAMSRA also includes ozone profiles from satellite retrievals. Most importantly for our study, in situ observations from ozone surface station networks are only assimilated in the CAMS Regional Ensemble. The quality with respect to observations in northern Fennoscandia will be discussed in Section~\ref{subsubsec:clim_ozone}. Without too much foreshadowing, the results prevented us from fetching the whole CAMSRA data.

>>>>

\subsection{NIBIO Environment Centre Svanhovd}
\label{subsec:svanhovd}
"Svanhovd is located beside the Pasvik river, in the middle of the wedge of Norwegian land separating Russia and Finland in the north. It is where the eastern Siberian taiga meets the western Boreal forest. [...] Svanhovd was originally established as a State Demonstration and Experimental Farm in the 1930's, in order to expand agriculture in Pasvik valley [...]" \citep[Svanhovd][]{NIBIO_Svanhovd}.

@@

\subsubsection{Atmospheric monitoring}
\label{subsubsec:atmo_svanvik}
For the growing seasons 2018/19, monitoring data of key variables (temperature, pressure, precipitation, and ozone) have been obtained from luftkvalitet.no which is operated by \citet{NILU_AIRQ}.

All agrometeorological variables including temperature and precipitation are available from September 1992 to present day \citep[LandbruksMeteorologiske Tjeneste][note the station name here is Pasvik]{LMT_NIBIO}.

@@

\subsubsection{Ozone garden}
\label{subsubsec:ozone_garden}
{\bf TODO: Details about the ozone garden and observed damage on ozone sensitive plants. We will need to come back to this in the discussion section after the Do3se modeling part.}
\begin{figure}
  \includegraphics[width=8.3cm]{IMG_7739.JPG}
  \caption{Clover in the Svanhovd ozone garden. The plants had to be secured against herbivores with a wire-mesh fence. The plants shown are approximately $6-12\,\unit{cm}$ in height.}
\end{figure}

@@

\subsubsection{Surface ozone observations}
\label{subsubsec:ebas}
All surface ozone observations used in this study are available from the EBAS database operated by \citet{NILU_EBAS}. In Table~\ref{tab:ebas_obs}, we give an overview over the exact locations and time range of operational data taking. All stations with available long term observations are located on higher ground than Svanhovd which will result in higher surface ozone concentrations in comparison as ozone abundance, in general, decreases with decreasing altitude in the absence of local precursors \citep[e.g.,][]{AB:Klingberg2009}. The periphery vegetation at all sites is similar and consists mainly of pine forests, birch, and heath. However, at close vicinity it varies substantially. Ozone measurements at Pallas are taken on top of mount Sammaltunturi $100\,\unit{m}$ above tree line (pine forest) and mainly consists of low vascular plants, mosses, and lichen \citep{BER:Hatakka2003}. At Svanhovd, the ozone measurements are taken amidst a meadow surrounded by agriculturally managed herbaceous plants and grass (c.c. Fig.\ref{fig:svanhovd_research_station}).

@@

Details of reanalysis data sets referred to in this work are listed in Table~\ref{tab:ozone_rea}.
There are two global reanalysis products available at the European Centre for Medium-Range Weather Forecasts (ECMWF) that include atmospheric tracers, in particular ozone (MACC and CAMSRA) \citep{ACP:Inness2013, ACP:Inness2019}. The temporal as well as spatial resolution of these reanalysis products is rather coarse: 3-hourly and $0.75^\circ\times 0.75^\circ$ or roughly $29.3\,\unit{km}\times 83.4\,\unit{km}$ at the location of Svanvik, respectively. In addition, higher resolution surface ozone reanalysis for whole Europe is available from Copernicus service for regional air quality control (note: since May 31st 2020 through the CAMS Atmosphere Data Store (ADS)). The regional air quality model reanalysis ensemble (CAMS regional Ensemble) is based on nine European state-of-the-art numerical air quality models \citep{Copernicus_Regio_AIRQ}. The ensemble mean is at fairly high spatial and temporal resolution compared to the global reanalysis from ECMWF: $0.1^\circ\times 0.1^\circ$ or roughly $3.9\,\unit{km}\times 11.1\,\unit{km}$ and 1-hourly, respectively. The covered time periods differ and no data are available for before the turn of the millennium. The CAMSRA and CAMS Regional Air Quality ensemble mean are available in near real time, but only former covers a period of sufficient length for climate analysis (2003 -- present). All reanalyses use different but, at that time, latest versions of the operational weather forecast system (OpenIFS) from ECMWF. They differ substantially in the assimilated observational ozone data. The MACC reanalysis assimilates only satellite derived tropospheric column ozone (TC), while CAMSRA also includes ozone profiles from satellite retrievals. Most importantly for our study, in situ observations from ozone surface station networks are only assimilated in the CAMS Regional Ensemble. The quality with respect to observations in northern Fennoscandia will be discussed in Section~\ref{subsubsec:clim_ozone}. Without too much foreshadowing, the results prevented us from fetching the whole CAMSRA data.
